Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-29 ms.tex
discussed line ratios in figure caption.

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
\caption{Example spectrum of \shStar\ near the Mg triplet.
{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
\end{centering}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
\caption{Example spectrum of \shStar\ near the Mg triplet.
{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
\end{centering}
\end{figure}
